\documentclass{article}

\usepackage{lipsum}
\usepackage[margin=2cm, left=2cm, includefoot]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}

% Header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}

\rhead{}
\lhead{}
\fancyfoot{}
\fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%

\begin{document}

\begin{titlepage}
	\begin{center}
		\line(1,0){500}\\
		[6mm]
		\huge{\bfseries Vision, Scope, Architectural Requirements and\\Software Architecture Design}\\
		\line(1,0){500}\\
		[5mm]
		\large\textbf{Project:}\\A World of Things\\
		[3mm]
		\large\textbf{Client:}\\Julian Hambleton-Jones\\
		[3mm]
		\large \textbf{Team:}\\Funge\\
		\line(1,0){500}\\
		[5mm]
		\large \textbf{Team Members:}\\
		[3mm]
		\large 14214742 - Matthew Botha\\
		\large 14446619 - Gian Paolo Buffo\\
		\large 14027021 - Matthias Harvey\\
        \large 14035538 - Dillon Heins\\[3mm]
	\end{center}
\end{titlepage}

\cleardoublepage
\thispagestyle{empty}
\tableofcontents
\cleardoublepage
\setcounter{page}{1}

\section{Vision}
The aim of this project is to build an innovative Internet of Things solution through the use of the Amazon Web Services Internet of Things hardware platform as well as the Amazon Web Services Cloud. No problem was formally defined and hence it was up to us to determine what solution we would be creating. We opted to create a solution which focuses on the education of students with regard to agriculture and plant sciences.\\\\
We plan to motivate students to become interested in agriculture by creating an "Internet of Plants". This involves the networking and monitoring of living plants in order to analyse aspects of their environment - such as water intake, lighting, humidity, moisture, mineral composition and temperature. These results will be used to create a collaborative platform on which users may share their own results and learn from the results of others, in order to grow the best possible plants. The main purpose of the platform is to encourage younger generations to become interested in agriculture and, in doing so, help stimulate South Africa's agricultural industry.\\\\
We plan to implement gamification on our platform as a way to encourage competition amongst users. Given enough time, we would like to automate more parts of the system - such as automated watering. Additionally, AI learning could be employed to optimise the conditions under which plants grow. By combining automation and AI learning, we could create an interesting challenge for the
users: Grow a plant better than our control plant grown with the help of AI.
\cleardoublepage

\section{Scope}

\cleardoublepage

\section{Architectural Requirements}
\subsection{Access and Integration Requirements}
\subsection{Quality Requirements}

\subsubsection{Maintainability}
The system should be designed and created in such a way that it easy to maintain in the future.
\begin{itemize}
	\item New developers should be able to easily understand the system
	\item It should be easy to modify parts of the system
	\item Adding new functionality should be easy and straightforward
\end{itemize}
\subsubsection{Flexibility}
It is important that the system has support for many hardware components such as sensors. These technologies are advancing rapidly, therefore it should be easy to add new components to the system, without making any large changes.
\subsubsection{Extensibility}
a program that it easy to modify parts of living plants in order to motivate students to model concurrent systems formally defined and learn from the
system dding new components such as sensors hese results of their own 
\subsubsection{Performance}
\subsubsection{Scalability}
\subsubsection{Security}
\subsubsection{Auditabilty}
\subsubsection{Usability}
\subsubsection{Testability}

\subsection{Architectural Responsibilities}
\subsection{Architecture Constraints}

\cleardoublepage

\section{Architecture Design}
\subsection{Architectural Tactics}
\subsection{Architectural Components Addressing Architectural Responsibilities}
\subsection{Infrastructure}
\subsection{Concepts and Constraints for Application Components}
\end{document}
